\documentclass{resume}

% \rohead{\thepage\ of \pageref{LastPage}}

\cofoot{
	\begin{spacing}{0.8}
%%	\so{Address, Line 2, City, ST 00000} \\
	\small{
%%		\footerphone{(555) 555-5555} \
		\footerlink{http://www.single-malt.co/} \
		\footeremail{willman.duffy@gmail.com}
	} \\
	% \small{\emph{
	% 	\LaTeX source for this resum$\acute{e}$ located at \href{https://github.com/philduffy/resume}{github.com/philduffy/resume}
	% }}
	\end{spacing}
}

\begin{document}

\name{Philip Willman Duffy}

\smallskip

\section{Skills}

\stdtable{
Languages  & \emph{Professional}: Ruby (Rails), JavaScript, HTML, CSS (Sass), SQL\\
					 & \emph{Testing}: Rails (Rspec and Minitest), JavaScript (Jasmine)\\
           & \emph{Hobby/Education}: C++, Bash, PHP, Perl\\
Tools      & Git, Sublime Text 3, Vim, OS X, Linux, VirtualBox, Zsh \\
Services   & Amazon S3, Digital Ocean, Heroku, Redis (Sidekiq and Resque)\\
Databases  & MySQL, PostgreSQL\\
}

\section{Relevant Experience}

\employer
	{Relay FM}
	{http://www.relay.fm/}
	{July 2014 --- \emph{Present}}
	{Freelance Consultant}
	{Worked with the client from Goodstuff.fm to adapt the podcast CMS to the needs of another client. Most of the core functionality remained intact but new challenges were added. The app was tweaked to be much more resistant to higher traffic numbers. On launch day the application received a peak of 1,000 requests per minute and maintained an average response time of 50ms during those peaks. Many of these changes were then backported to the original parent application.}
\\ \\ \\
\employer
	{Goodstuff.fm}
	{http://www.goodstuff.fm/}
	{January 2014 --- \emph{Present}}
	{Freelance Consultant}
	{Acted as the sole backend developer on a Podcast CMS. Created a fully functional application complete with S3 storage integration for mp3s and images, a protected management area, RSS feed generation, automatic posting to Twitter for new episodes and a complete test suite that runs in less than ten seconds. Tapped into Carrierwave's uploader functionality to create a feature that overwrites id3 tags and album artwork on mp3s when uploaded. This happens on the fly while uploading to Amazon S3. Generated an iTunes compatible podcast RSS feed for each unique podcast. The entire CMS backend was done in roughly 20 hours of work.}
\\ \\ \\
\employer
	{WeSpire}
	{http://www.wespire.com/}
	{September 2011 --- \emph{Present}}
	{Full Stack Developer}
	{Responsible for developing and helping architect a leading edge corporate sustainability and engagement platform with the Ruby on Rails framework. Developed and architected hundreds of features while utilizing test driven development in an agile environment. Became known as the maintainer of the MiniTest test suite through my eternal battle to keep the test suite run time under 3 minutes. Also championed the use of a CI server and SimpleCov to track test coverage. Acted primarily as a backend developer but spent a large portion of my time filling in as a front end developer as needed. I created the front-end style guide as it exists today and helped make sure that all code review was held up to its standards. Converted the entire application from a split mobile web app to a responsive app by myself in 2 weeks.}
\\ \\ \\
\employer
	{Terrible Labs}
	{http://www.terriblelabs.com/}
	{August 2011 --- May 2012}
	{Junior Developer}
	{Worked with multiple clients on Ruby on Rails projects with features that were designed with test-driven development. Created web-based HTML5 mobile applications with a backbone.js front-end and Ruby on Rails. Worked both remotely and in-house at startups and kept track of all work done with GitHub issues and Pivotal Tracker.}
\\ \\ \\
\employer
	{Harvard University}
	{http://www.harvard.edu/}
	{January 2011 --- May 2011}
	{IT Intern}
	{Developed and distributed unique images for specialty machines in the Harvard College Libraries. Fulfilled all client requests and managed them through DK Help Desk. Diagnosed and remedied issues with LANDesk Remote Agent system. Helped facilitate the upgrade of over one hundred staff machines.}

\section{Side Projects}

\project
	{Sorta}
	{http://www.sortalist.com/}
	{Creator}
	{An application built over a week in Rails that allows users to register and build sortable lists of their favorite movies, tv shows, music and books.}

\section{Education}

\stdtable{
School              & Wentworth Institute of Technology Boston, MA\\
Degree              & Bachelor of Science in Computer Networking\\
}

\end{document}
